Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-09 paper.tex
Revising the introduction
refs #21 but also #19

***TO DO***: complete this considering the new contents and results\\

Publishing a book, as releasing any other cultural product with a
physical substrate, implies several
types of risks and costs due to
the complexity, and derived expenses, of the production and
distribution processes.  When a company is faced with the problem or
releasing a completely new product, in the sense that it is an unknown
author or a new topic with no track record, sales forecasts can
only be based on the experience obtained from other similar products,
but the definition of ``similar'' itself is obscure and, sometimes,
subjective. Even if it is a known author or topic, having accurate
estimations of future sales of the new 
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales by too much. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
%which should be obvious from the get go, don't know why you need 4
%papers to affirm that - JJ

@@

Thus, it is extremely important to develop an accurate predictive method
which could accurately forecast the future sales a new book will
achieve, in order to optimise production, improve the publishing
company profits or minimise losses \cite{Zhao2001}. This is the main
objective of this paper. 
%FERGU: entonces el objetivo es desarrollar una herramienta? La metodología? Dejarlo más claro en todos los sitios
An example is the optimisation of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir
% un poco más lo que se hace en ese trabajo. ;)
% An example of what? Does that go there? - JJ

However, designing such an accurate predictive tool is a difficult
task in this scope, as book sales are influenced by several factors
that make them fluctuate and, moreover, usually they might be not
controllable and even unknown. 
%FERGU: "moreover, usually" son dos adverbios juntos y queda un poco raro 
For instance, some are related to decisions on purchases, others with freight 
%FERGU: some factors para dejarlo claro
traffic, or others with the distribution strategy \cite{Little1998}. % This paragraph is rather useless - JJ

@@

In the research published in this paper, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for bookshops,
% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
publishers and distributors. 
Usually, the company's expert sales managers analysed historical data 
and applied their knowledge using external variables to compute
correct estimations (predictions), for instance, she can decide
increasing or decreasing the sales prediction based on season or sales
period.                         % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as a human expert,
may lead to a `fuzzy-like' analysis, which may not take all the variables into account. 
%FERGU: fuzzy-like existe? suena raruno :P
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}.

For these reasons, the industry requires the best suited forecasting
techniques to be adopted so that, estimating sales task is carried out
reliably, accurately, and in an automatic way. % Iterative. Another
                                % useless paragraph - JJ

@@

***TO DO***: rewrite this considering the new structure of the paper\\

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the 
problem of how many books should be printed when a new book is published, 
        % no es el problema de publicación, es el problema de venta
        % de libros sin publicar. Habrá que buscar un nombre - JJ
        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
 followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  %FERGU: mejor described para no repetir
Section \ref{sec:experiments} reports and analyses the obtained results with a 
real dataset. Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}. 
% Antonio - TODO: rescribir con los contenidos finales del artículo. ;)

>>>>

%***TO DO***: complete this considering the new contents and results\\
% Instead of just writing this you should say what has changed and
% what should be changed. For instance, the paragraph below probably
% shouldn't - JJ 
Publishing a book, in the same way as releasing any other cultural product with a
physical substrate, implies several
types of risks and costs due to
the complexity, and derived expenses, of the production and
distribution and storage processes.  When a company is faced with the problem or
releasing a completely new product, in the sense that it is an unknown
author or a new topic with no track record, sales forecasts can
only be based on the experience obtained from other similar products,
but the definition of ``similar'' itself is obscure and, sometimes,
subjective. Even if it is a known author or topic, having accurate
estimations of future sales of the new 
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales by too much. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
%which should be obvious from the get go, don't know why you need 4
%papers to affirm that - JJ

@@

Thus, it is extremely important to develop an accurate predictive method
which could forecast the future sales a new book will
achieve, in order to optimise production schedules, improve the publishing
company profits or minimise losses \cite{Zhao2001}. This is the main
objective of this paper. 
%FERGU: entonces el objetivo es desarrollar una herramienta? La
%metodología? Dejarlo más claro en todos los sitios
% Un método predictivo. Lo deja muy claro - JJ
An example is the optimisation of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir
% un poco más lo que se hace en ese trabajo. ;)
% An example of what? Does that go there or to the state of the art? - JJ

The accuracy of the predictive method we intend to design is affected
negatively by several factors, related to decisions on purchases, to freight 
traffic, or with the distribution strategy \cite{Little1998}. % This
                                % paragraph is rather useless - JJ
% I have changed the paragraph completely, but still don't know what
% this is doing here - JJ

@@

In the research published in this paper, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for bookshops,
publishers and distributors. 
Usually, the company's expert sales managers analysed historical data 
and applied their knowledge using external variables to compute
correct estimations (predictions), for instance, she can decide
increasing or decreasing the sales forecast based on season or sales
period.                          
However, carrying out the analysis and forecasting process as a human expert,
may lead to imprecise predictions which may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}. A
initial version of this method was developed under contract with that
company and eventually integrated in their product. This paper
represents an improved version of that method based on the same data.

@@

%***TO DO***: rewrite this considering the new structure of the paper\\

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the 
problem of how many books should be printed when a new book is published, 
followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  Section \ref{sec:experiments} reports and analyses the obtained results with a 
real dataset. Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}. 
% Antonio - TODO: rescribir con los contenidos finales del artículo. ;)
